Results publications are inadequately linked to trial registrations: An automated pipeline and evaluation of German university medical centers

### 2021-09-07 docs/manuscript/manuscript.Rmd
Change upset plot, remove registry and change to percent

Per our inclusion criteria all trials in our sample (n = `r n_trials_ft`) were registered and had a publication, however only `r report_trials(n_trials_link_full)` trials had the most comprehensive registration-publication linking, meaning the publication linked in the registration as well as the TRN in the publication full-text, abstract, and PubMed metadata. Disregarding metadata, which is largely beyond trialists' control, an additional `r n_trials_link_ft_abs_reg - n_trials_link_full` trials had comprehensive linking for a total of `r report_trials(n_trials_link_ft_abs_reg)`. An additional `r report_trials(n_trials_link_ft_abs - n_trials_link_ft_abs_reg)` met the CONSORT and ICMJE guidelines to include TRNs in both the full-text and the abstract. In contrast, we found `r report_trials(n_trials_link_none)` trials with no links in either the registration or the publication. The most common linking practice was reporting of the TRN in the full-text only, accounting for `r report_trials(n_trials_link_ft_only)` trials. The inclusion of the various link types ranged from `r inline_text(tbl_link_by_reg, has_iv_trn_abstract, stat_0)` in abstracts to `r inline_text(tbl_link_by_reg, has_iv_trn_ft, stat_0)` in full-text. Table \@ref(tab:tbl-link-by-reg) shows registration-publication links overall and by registry. <!--# point estimates in table should have CI, right? -->Figure \@ref(fig:plot-upset-links-reg-pub-registries) shows the intersection of registration-publication links across the various types for ClinicalTrial.gov and DRKS trials.<!--#shows the number of trials with each link type and combination of link types, overall and by registry.--> As PubMed incorporated DRKS as a databank source in 2014, Supplemental Table \@ref(tab:app-tbl-link-by-reg-2014) shows the linking practices in trials published as of 2014 (n = `r inline_text(tbl_link_by_reg_2014, has_iv_trn_secondary_id, stat_0, pattern = "{N}")`), which reflect similar rates to Table \@ref(tab:tbl-link-by-reg) [@nationallibraryofmedicine2018].

@@

```{r plot-upset-links-reg-pub-registries, fig.cap = "Trials with all combinations of links between registration and publication in ClinicalTrials.gov and DRKS", out.width="80%"}
knitr::include_graphics(path(dir_figures, "plot-upset-link-type.pdf"))
```

>>>>

Per our inclusion criteria all trials in our sample (n = `r n_trials_ft`) were registered and had a publication, however only `r report_trials(n_trials_link_full)` trials had the most comprehensive registration-publication linking, meaning the publication linked in the registration as well as the TRN in the publication full-text, abstract, and PubMed metadata. Disregarding metadata, which is largely beyond trialists' control, an additional `r n_trials_link_ft_abs_reg - n_trials_link_full` trials had comprehensive linking for a total of `r report_trials(n_trials_link_ft_abs_reg)`. An additional `r report_trials(n_trials_link_ft_abs - n_trials_link_ft_abs_reg)` met the CONSORT and ICMJE guidelines to include TRNs in both the full-text and the abstract. In contrast, we found `r report_trials(n_trials_link_none)` trials with no links in either the registration or the publication. The most common linking practice was reporting of the TRN in the full-text only, accounting for `r report_trials(n_trials_link_ft_only)` trials. The inclusion of the various link types ranged from `r inline_text(tbl_link_by_reg, has_iv_trn_abstract, stat_0)` in abstracts to `r inline_text(tbl_link_by_reg, has_iv_trn_ft, stat_0)` in full-text. Table \@ref(tab:tbl-link-by-reg) shows registration-publication links overall and by registry. <!--# point estimates in table should have CI, right? -->Figure \@ref(fig:plot-upset-links-reg-pub) shows the percentage of trials with each combination of links between registration and publication.<!--#shows the number of trials with each link type and combination of link types, overall and by registry.--> As PubMed incorporated DRKS as a databank source in 2014, Supplemental Table \@ref(tab:app-tbl-link-by-reg-2014) shows the linking practices in trials published as of 2014 (n = `r inline_text(tbl_link_by_reg_2014, has_iv_trn_secondary_id, stat_0, pattern = "{N}")`), which reflect similar rates to Table \@ref(tab:tbl-link-by-reg) [@nationallibraryofmedicine2018].

@@

```{r plot-upset-links-reg-pub, fig.cap = "Percentage trials with each combination of links between registration and publication", out.width="80%"}
knitr::include_graphics(path(dir_figures, "plot-upset-link-type.pdf"))
```
